\documentclass[12pt]{amsart}
\pagestyle{plain}

\usepackage{amsthm, setspace, framed, hyperref}
\usepackage[pdftex]{graphicx}
\usepackage{enumerate}
\usepackage[none]{hyphenat}

\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\setlength\parindent{0pt}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem*{cor}{Corollary}
\newtheorem{quest}{Question}
\theoremstyle{definition}
\newtheorem*{defn}{Definition}
\newtheorem*{ex}{Example}

\begin{document}
\title[]{Cryptography Mission 10 Dossier}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l}
MATH/CSCI 408  & Name: \rule{7cm}{0.5pt} \\
\hline\hline
\end{tabular*} \\
\maketitle

\begin{center}\textbf{Deadline: Thursday, 1 December 2016 at 3:05pm}\\

This mission covers Sections 7.5, 9.1, and 9.2.
\end{center}

\begin{framed}
Check one:\\

\framebox(12,12){} I received help from the following classmate(s) on this assignment:\\

\rule{15cm}{0.5pt}.\\

\framebox(12,12){} I did not receive any help on this assignment.
\end{framed}

\section{Graded Problems}

\begin{enumerate}[1.]
	\item Work through the code on Dr. Kate Stange's cryptography website: \url{http://crypto.katestange.net/solutions-to-discrete-log-practice-session/}.  
		\begin{enumerate}[a.]
			\item What is $L_5(11) \bmod 197$?
			\begin{framed}
			\vspace{.5in}
			\end{framed}
			\item What is $L_5(10) \bmod 197$?
			\begin{framed}
			\vspace{.5in}
			\end{framed}
		\end{enumerate}
	\item (RSA Signature) Suppose a message is $m = 12$.  It is publicly known that $e_A = 7$ and $n = 253$.
			\begin{enumerate}[a.]
			\item If Bob receives the information $y = 81$.  Compute $z \equiv y^{e_A} \bmod n$.  Did Alice sign the document or not?  Justify.
			\begin{framed}
			\vspace{1.5in}
			\end{framed}
			\newpage \item Suppose that Bob receives the information $y = 100$ instead.  Again, compute $z$.  Did Alice sign the document or not?  Justify.
			\begin{framed}
			\vspace{1.5in}
			\end{framed}
		\end{enumerate}
	\item Fill out the course evaluations (in your g.coastal.edu email). Please write meaningful and specific feedback.  I will read these to improve my teaching, and they are also used as a way to evaluate how I'm doing at my job.\\
	Things to keep in mind: which activities did you like most and which worked best?  Did you feel like I tried to address your questions throughout the semester?  Which aspects of class do you think can be improved upon?  \textbf{Forward the confirmation email to me to get two points for this mission.}\\
	
	\item (Optional) I won't see the course evaluations until much later.  If you'd like to give some specific feedback now, please do so.  In particular, I'd like to hear back about the following questions:
	\begin{itemize}
		\item Do you feel like we had a sufficient balance of math and computer science topics?
		\item What did you think of the Escape Room activity?
		\item What did you think of the Current Issues debate?
		\item Do you think there was a sufficient mix of teaching styles in the class (e.g. lectures, group work time, presentations)?
		\item What is something that you will take away from this class after 10 years?
	\end{itemize}
	\begin{framed}
	\vspace{1.5in}
	\end{framed}
	
\end{enumerate}


\section{Recommended Exercises}
\noindent These will not be graded but are recommended if you need more practice.
\begin{itemize}
	\item Section 7.6 \# 5, 7, 11
	\item Section 7.7 \# 2, 3
	\item Section 9.6 \# 1, 2
	\item Section 9.7 \# 1
\end{itemize}
	
\end{document}
